---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# serosolver

`serosolver` is a modelling and inference package that uses a dynamic model to infer antibody dynamics and infection histories from cross-sectional or longitudinal serological data. The model infers individual-level infection histories, historical attack rates, and patterns of antibody dynamics by accounting for cross-reactive antibody responses and measurement error.

## Installation

1. Install [R][r-project]

2. Install the development version of serosolver from [GitHub](https://github.com/seroanalytics/serosolver):

```{r installation,eval=FALSE}
devtools::install_github("seroanalytics/serosolver")
library(serosolver)
```

## Quick start and vignettes

Read the [quick start vignette][vignette-doc] to set up and run a simple implementation with a simulation model.

There are additional Rmarkdown vignettes for [Case Study 1][c1-vignette-doc] (longitudinal analysis of influenza A/H1N1p in Hong Kong) and [Case Study 2][c2-vignette-doc] (cross-sectional analysis of influenza A/H3N2 in Guangzhou Province, China), to accompany the analysis in the serosolver paper.

[r-project]: http://cran.r-project.org
[vignette-doc]: https://seroanalytics.github.io/serosolver/articles/serosolver-quick_start_guide.html
[c1-vignette-doc]: https://seroanalytics.github.io/serosolver/articles/cs1_vignette.html
[c2-vignette-doc]: https://seroanalytics.github.io/serosolver/articles/cs2_vignette.html
